\textsf{Are frontier models superhuman chemists?}

### 2024-03-19 src/tex/ms.tex
try heatmap

\begin{figure}
    \centering
    \includegraphics{figures/all_questions_models_completely_correct_radar_human.pdf}
    \caption{\textbf{Performance of the models and humans on the different topics of the \chembench corpus.} The radar plot shows the performance of the models and humans on the different topics of the \chembench corpus. The performance is measured as the fraction of questions that were answered completely correctly by the models.}
    \label{fig:all_questions_models_completely_correct_radar_human}
    \script{analyze_model_reports.py}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics{figures/all_questions_models_completely_correct_radar_human.pdf}
    \caption{\textbf{Performance of the models and humans on the different topics of the \chembench corpus.} The radar plot shows the performance of the models and humans on the different topics of the \chembench corpus. The performance is measured as the fraction of questions that were answered completely correctly by the models.
    This figure shows the performance on the subset of questions that was answered by humans, too. The performance of models on the entire corpus is shown in \Cref{fig:performance_per_topic}.
    }
    \label{fig:all_questions_models_completely_correct_radar_human}
    \script{analyze_model_reports.py}
\end{figure}
